---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(autoReg)
```

# 1. Prescreening
## 1-1.Check data
The `check_data()` function checks if the response variable is binary or continuous. If the  response variable is categorical (factor or character with two levels), it changes the response variable into binary(0 or 1).

**Example**
```{r}
result <- check_data(X = bin.x, y = bin.y)
result$response_type
nrow(result$y)
```
**Output**

- `response_type`: Type of response variable y (`"binary"` or `"continuous"`)
- `y`: finalized response value of y in vector


## 1-2. Split train and test data
The `train_test()` function generates train and test data for machine learning. In addition to matrix `X` and vector `y`, the user is required to determine `p`, which is the proportion of the training data. If `p` is not given, it splits the train and test data by a proportion of 0.8.

**Example**
```{r}
traintest <- train_test(X = bin.x,y = bin.y, p = 0.8)
nrow(traintest$train_X)
nrow(traintest$test_X)
```

**Output**

- `train_X`: A matrix of predictor variables in train data
- `train_y`: A vector of response variable in train data
- `test_X`: A matrix of predictor variables in test data
- `test_y`: A vector of response variable in test data


## 1-3. Determine informative predictors
The `prescreening()` function performs pre-screening on the predictor variable, evaluating which predictor variable is most informative based on the absolute value of correlation to the response variable. In addition to matrix `X` and vector `y`, users are required to determine `K`, the number of informative predictors. `K` is set to 5 by default. 

**Example**
```{r}
prescreening(X = bin.x, y = bin.y,K = 5)
```

**Output**  

- Names of the K most informative predictors



# 2. Fitting model
Fitting different types of models is a fundamental task in data analysis and machine learning. This package provides a rich ecosystem of packages for fitting various types of modes. This tutorial covers how to fit the following models using built-in datasets in the package.  

1. Linear model
2. Logistic model
3. Ridge model
4. LASSO model
5. Elastic net model


## 2-1.Standard regression model
`fitStandard()` function allows users to fit standard regression model. It will perform linear regression if the response vector `y` is continuous and logistic regression if `y` is binary. 

**Example: Continous response**
```{r}
fitStandard(X = cont.x, y = cont.y)
```

**Output**

- An object of a linear regression model

**Example: Binary response**  
```{r, warning = FALSE}
fitStandard(X = bin.x, y = bin.y)
```

**Output**  

- An object of a logistic regression model


## 2-2. Ridge regrssion model
`fitRidge()` function allows users to fit a ridge regression model.  

**Example**  
```{r}
fitRidge(X = bin.x, y = bin.y)
```

**Output**  

- An object of a ridge regression model


## 2-3. LASSO regression model
`fitLasso()` function allows users to fit an LASSO regression model. 

**Example**  
```{r}
fitLasso(X = cont.x, y = cont.y)
```

**Output**  

- An object of a LASSO regression model


## 2-4. Elastic net model
`fitElasticNet()` function allows users to fit an elastic net model. 

**Example**  
```{r}
fitElasticNet(X = bin.x, y = bin.y)
```

**Output**  

- An object of an elastic net regression model


## 2-5. Evaluation of single regression model
Users can evaluate the performance of single regression model by `evaluateModel()` function. Users must specify regression model to evaluate among `"standard"`, `"ridge"`, `"lasso"`, and `"elastic.net"` in `model` parameter. If the parameter `model` is not specified, the function will automatically evaluate performance of standard regression model. A parameter `p`, which is the proportion of train and test data, is set to 0.8 by default. 

**Example: Binary Response**
```{r, warning = FALSE}
evaluateModel(X = bin.x, y = bin.y, model = "standard", p = 0.8)
```

**Output**  

- `confusion.matrix`: Confusion matrix comparing final predictions and true test labels
- `accuracy`: Overall classification accuracy

**Example: Continuous Response**
```{r}
evaluateModel(X = cont.x, y = cont.y, model = "standard", p = 0.8)
```

**Output**

- `r_squared`: R-squared value, which is also known as coefficient of determination
- `RMSE`: Root Mean Square Error between final predictions and test responses



# 3. Bagging
Bootstrap bagging is a technique used to improve the stability and accuracy of machine learning algorithms, especially those prone to high variance. It involves training multiple models on different subsets of the training data and then combining their predictions to make more robust predictions. 

## 3-1. Bagging standard regression model
The `baggingStandard()` function generates a standard regression model(linear for continuous response and logistic for binary response) regarding selected samples and collects the coefficients of each model. A parameter `R`, the number of replicates for the bootstrap process, is set to 50 by default. The final model is generated by computing the means of the coefficients. 

**Example: Binary Response**
```{r, warning = FALSE}
baggingStandard(bin.x, bin.y, R=50)
```

**Example: Continuous Response**
```{r}
baggingStandard(cont.x, cont.y, R=50)
```

**Output**  

- `coef`: Coefficients of final bagged model by averaging coefficients from each iteration
- `sd.coef`: Standard deviation of each coefficient in final bagged model. 
- `pos.rate`: Sign consistency rate of each coefficient


## 3-2. Bagging ridge model
The `baggingRidge()` function generates a ridge model regarding selected samples for selected iterations and collects the coefficients of each model. A parameter `R`, the number of replicates for the bootstrap process, is set to 50 by default. The final model is generated by computing the means of the coefficients. 

**Example**
```{r}
baggingRidge(cont.x, cont.y, R = 50)
```

**Output**  

- `coef`: Coefficients of final bagged model by averaging coefficients from each iteration  
- `sd.coef`: Standard deviation of each coefficient in final bagged model


## 3-3. Bagging LASSO model
The `baggingLasso()` function generates a LASSO model regarding selected samples for selected iterations and collects the coefficients of each model. A parameter `R`, the number of replicates for the bootstrap process, is set to 50 by default. The final model is generated by computing the means of the coefficients. 

**Example**
```{r}
baggingLasso(cont.x, cont.y, R = 50)
```

**Output**  

- `coef`: Coefficients of final bagged model by averaging coefficients from each iteration  
- `selection.rate`: Selection frequency of each predictors


## 3-4. Bagging elastic net model
The `baggingElasticNet()` function generates an elastic net model regarding selected samples for specified iterations and collects the coefficients of each model. A parameter `R`, the number of replicates for the bootstrap process, is set to 50 by default. The final model is generated by computing the means of the coefficients. 

**Example**
```{r}
baggingElasticNet(cont.x, cont.y, R = 50)
```

**Ouput**

- `coef`: Coefficients of final bagged model by averaging coefficients from each iteration    
- `sd.coef`: Standard deviation of each coefficient in final bagged model  
- `selection.rate`: Selection frequency of each predictors


## 3-5. Evaluation of bootstrap bagging process 
Users can evaluate performance based on the bootstrap bagging model by `evaluateBagging()` function. Users must specify `model` parameter to decide regression model for bootstrap bagging among following list: `"standard"`, `"ridge"`, `"lasso"`, and `"elastic.net"`. If not specified, the function automatically performs and evaluates bootstrap bagging in standard regression model. This function divides train and test data. A parameter `p`, which is the proportion of train and test data, is set to 0.8 by default. Then, users are given selections for which model to perform the bagging process. A parameter `R`, the number of replicates for the bootstrap process, is set to 50 by default. 

**Example: Binary Response**
```{r, warning = FALSE}
evaluateBagging(bin.x, bin.y, model = "standard", R = 50, p = 0.8)
```

**Output**  

- `confusion.matrix`: Confusion matrix comparing final predictions and true test labels
- `accuracy`: Overall classification accuracy

**Example: Continuous Response**
```{r}
evaluateBagging(cont.x, cont.y, model = "standard", R = 50, p = 0.8)
```

**Output:**

- `r_squared`: R-squared value, also known as coefficient of determination
- `RMSE`: Root Mean Square Error between final predictions and test responses




# 4. Ensemble Learning
Ensemble learning is a powerful statistical approach that combines the predictions of multiple individual models to improve overall accuracy and robustness compared to any single model used in isolation. The `ensemblelearning()` function implements this concept by allowing users to interactively select and train a variety of regression and classification models, including general regression (linear, logistic) and regularized regression techniques. After the user finishes selecting their desired suite of models, the function aggregates their outputs through an averaging process to generate final predictions for the test dataset. Depending on whether the response variable is binary or continuous, the function concludes by providing comprehensive performance metrics such as accuracy and confusion matrices or R-squared and RMSE.

**Example: Binary Response**  
```{r, eval = FALSE}
ensembleLearning(bin.x, bin.y, p = 0.8)
```

During execution, users will be prompted to select models interactively:  
```text
Choose a model.
  1 for standard regression,
  2 for ridge,
  3 for LASSO,
  4 for elastic net,
  5 to exit.
```
Users can enter an integer between 1 and 4 to select regression model. This function will repeat unless users enter 5 to terminate the ensemble learning. 

**Output**  

- `model_summary`: Table for count of regression model used in ensemble learning process
- `confusion.matrix`: Confusion matrix comparing final predictions and true test labels
- `accuracy`: Overall classification accuracy

**Example: Continuous Response**
```{r, eval=FALSE}
ensembleLearning(cont.x, cont.y, p = 0.8)
```

During execution, users will be prompted to select models interactively:
```text
Choose a model.
  1 for standard regression,
  2 for ridge,
  3 for LASSO,
  4 for elastic net,
  5 to exit.
```
Users can enter an integer between 1 and 4 to select regression model. This function will repeat unless users enter 5 to terminate the ensemble learning. 

**Output:**

- `model_summary`: Table for count of regression model used in ensemble learning process 
- `RMSE`: Root Mean Square Error (RMSE) between final predictions and test responses
- `r-squared`: R-squared, also known as coefficient of determination



